Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-06 paper.tex
Missing line from section 3, paragraph 4
Added visualisation references

Finally, the distribution of queries on public holidays is observed to deviate from that of an average day. 
Figure 3 provides a breakdown of queries per hour on Christmas eve, 24th December 2015, in comparison to an average Thursday of the same year. 
As illustrated, the evening peak on Christmas eve occurs earlier than that of an average Thursday. 
For these reasons, we believe that route planning query data maybe a viable source of information for flow analysis.

@@

Visualization is crucial for making the analysis tangible, so that results can be communicated and debated \todo{Robinson, 2008 -121}. 
This is key for our research since the questions presented are exploratory in nature \todo{Kraak, 2008 -150} and can be addressed in many ways. 
Movement data has received substantial attention from the visualisation community and a range of techniques has been developed to support analysis \todo{Andrienko, 2012 -196}. 
Of these techniques, flow visualisations are commonly employed to facilitate the comparison of aggregated movement. 
Flow visualisations can be broadly categorized into two groups. Representations that preserve the complete trajectory and OD type representations that take only the start and end locations into account.
Since our data solely consists of OD information, we narrow our description to the latter group of visualisation techniques.

@@

The pair of chord diagrams in \cref{fig:brussels,fig:antwerp} capture the aggregated number of queries made between any two stations on weekdays and weekends between 6 to 9 in the morning.
The chords that link two distinct stations, are coloured coded by region and proportionately scaled to the number of queries from a station of origin to a destination.
For instance, approximately 3,530 queries were made from Leuven to Brussels than in the opposite direction (approximately 1,530) on weekdays.
Reading both diagrams in this manner reveals the complexity of movement on the rail system and the significance of cities in daily travel.
Brussels serves as the principal centre of rail activity in general, yet its centrality is more distinctive for the walloon region than Flanders.
Queries from Walloonia with exception to Liege, are generally made from provincial stations towards Brussels instead of their respective provincial capitals.
Queries in Flanders, on the hand, tend to be distributed among major cities otherwise known as the Flemish Diamond, a network of four metropolitan areas in Belgium comprised of Ghent, Brussels, Antwerp and Leuven.
The difference between both patterns appear to correspond with existing measures of population density, providing valuable insight and alternative perspectives into the function of cities in rural and urban settings.

>>>>

Finally, the distribution of queries on public holidays is observed to deviate from that of an average day. 
Figure 3 provides a breakdown of queries per hour on Christmas eve, 24th December 2015, in comparison to an average Thursday of the same year. 
As illustrated, the evening peak on Christmas eve occurs earlier than that of an average Thursday. 
For these reasons, we believe that route planning query data maybe a viable source of information for flow analysis. \todo{where people are heading between certain time intervals?}

@@

Visualization is crucial for making the analysis tangible, so that results can be communicated and debated \cite{robinson2008collaborative}. 
This is key for our research since the questions presented are exploratory in nature \cite{kraak2008exploratory} and can be addressed in many ways. 
Movement data has received substantial attention from the visualisation community and a range of techniques has been developed to support analysis \cite{andrienko2012visual}. 
Of these techniques, flow visualisations are commonly employed to facilitate the comparison of aggregated movement. 
Flow visualisations can be broadly categorized into two groups. Representations that preserve the complete trajectory and OD type representations that take only the start and end locations into account.
Since our data solely consists of OD information, we narrow our description to the latter group of visualisation techniques.

@@

The pair of chord diagrams in \cref{fig:brussels,fig:antwerp} capture the aggregated number of queries made between any two stations on weekdays and weekends between 6 to 9 in the morning.
The chords that link two distinct stations, are coloured coded by region and proportionately scaled to the number of queries from a station of origin to a destination.
For instance, approximately 3,530 queries were made from Leuven to Brussels than in the opposite direction (approximately 1,530) on weekdays.
Reading both diagrams in this manner reveals the complexity of movement on the rail system and the significance of cities in daily travel.
Brussels serves as the principal centre of rail activity in general, yet its function as a centre is more distinctive for the walloon region than Flanders.
Queries from Walloonia with exception to Liege, are generally made from provincial stations towards Brussels instead of their respective provincial capitals.
Queries in Flanders, on the hand, tend to be distributed among major cities otherwise known as the Flemish Diamond, a network of four metropolitan areas in Belgium comprised of Ghent, Brussels, Antwerp and Leuven.
The difference between both patterns appear to correspond with existing measures of population density, providing valuable insight and alternative perspectives into the function of cities in rural and urban settings.
